Differential abundance analysis of taxonomically-biased microbiome measurements

### 2022-05-23 index.Rmd
Revise title
Add link to research notebook to preface

---
title: "Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Jacob T. Nearing^[Dalhousie University]
  - Amy D. Willis^[University of Washington]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
# For pandoc latex processing
documentclass: article
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
output:
  bookdown::gitbook:
    css: style.css
    number_sections: true
    includes:
      in_header: header.html
    config:
      sharing:
        facebook: no
        github: yes
        twitter: no
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  bookdown::pdf_book:
    includes:
      in_header: latex/preamble.tex
    keep_tex: true
    dev: "pdf"
    papersize: letter
    toc_depth: 2
    toc_unnumbered: yes
    toc_appendix: yes
---

@@

This manuscript addresses the effect that the taxonomic bias inherent in microbiome measurement has on microbial differential-abundance analysis.
We describe the basic problem posed by taxonomic bias for measuring changes in the abundance of particular taxa across conditions and describe new strategies for mitigating the errors it induces.
Analyses of both relative and absolute abundances are considered.
The manuscript is licensed under a [CC BY 4.0 License](https://creativecommons.org/licenses/by/4.0/).
See [the Zenodo record](https://doi.org/10.5281/zenodo.4552717) for how to cite the latest version.

>>>>

---
title: "Differential abundance analysis of taxonomically-biased microbiome measurements"
author:
  - Michael R. McLaren^[North Carolina State University; send correspondence to m.mclaren42@gmail.com]
  - Jacob T. Nearing^[Dalhousie University]
  - Amy D. Willis^[University of Washington]
  - Karen G. Lloyd^[University of Tennessee]
  - Benjamin J. Callahan^[North Carolina State University]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
bibliography: [main.bib, packages.bib]
biblio-style: apalike
link-citations: yes
# description:
# For pandoc latex processing
documentclass: article
geometry:
  - top=1in
  - bottom=1in
  - left=1.5in
  - right=1.5in
output:
  bookdown::gitbook:
    css: style.css
    number_sections: true
    includes:
      in_header: header.html
    config:
      sharing:
        facebook: no
        github: yes
        twitter: no
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
  bookdown::pdf_book:
    includes:
      in_header: latex/preamble.tex
    keep_tex: true
    dev: "pdf"
    papersize: letter
    toc_depth: 2
    toc_unnumbered: yes
    toc_appendix: yes
---

@@

This manuscript addresses the effect that the taxonomic bias inherent in microbiome measurement has on microbial differential-abundance analysis.
We describe the basic problem posed by taxonomic bias for measuring changes in the abundance of particular taxa across conditions and describe new strategies for mitigating the errors it induces.
Analyses of both relative and absolute abundances are considered.
The manuscript is licensed under a [CC BY 4.0 License](https://creativecommons.org/licenses/by/4.0/).
See [the Zenodo record](https://doi.org/10.5281/zenodo.4552717) for how to cite the latest version.
Supporting data analyses can be found in the accompanying [computational research notebook] (https://mikemc.github.io/differential-abundance-theory/notebook/).
